Measurement of the positive kaon-argon total hadronic differential cross section in the LArIAT experiment

### 2018-03-18 Chapter-4/3-KaonInteractionsInLAr.tex
s

Let us start by discussing the uncertainty on $E_{Beam}^{kin}$. Since we are assuming a beam of pions, the uncertainty on the value of mass of the pion ($m_{Beam}$) as given by the pdg is irrelevant compared to the momentum uncertainties, thus $\delta E_{Beam}^{kin} = \delta p_{Beam}^{kin}$. \textcolor{blue}{Ideas on how to estimate the momentum uncertainty. Base line:  4-points track. In case of 3-points track, add an additional 2\%. }

KEWC = (pWC2 - m2)?   => ?m very small, ?KEWC = ?pWC
ELOSS                        => ?ELOSS MC truth spread
dE/dxi                  => ?dE/dxi MC Reco - Data comparison
dxi                        => ?dxi      MC Reco - Data comparison
?TOT, ?i<j                  => Efficiency correction

>>>>

Let us start by discussing the uncertainty on $E_{Beam}^{kin}$. Since we are assuming a beam of pions, the uncertainty on the value of mass of the pion ($m_{Beam}$) as given by the pdg is irrelevant compared to the momentum uncertainties, thus $\delta E_{Beam}^{kin} = \delta p_{Beam}^{kin}$. 
We estimate the momentum uncertainty as follows.

\textcolor{blue}{  
We estimate the uncertainty on a 4-point track. In case of 3-points track, we add an additional 2\% coming from Greg's study. 
Uncertainty on a 4-point track:
\begin{itemize}
\item[-]  Alignment surveys. 1mm misalignment translates to 3\% in overall
\item[-] Doug study dp/p = ~2\% based on field map (docdb 1710)
\item[-] Minerva test beam paper
\end{itemize}
}

We estimate the uncertainty on the energy loss between the beamline momentum measurement and the TPC, $E_{loss}$, using the DDMC pion sample. We shoot pions from WC4 with the same momentum distribution as in the beamline data and plot the true $E_{loss}$ for that sample. The width of the $E_{loss}$ distribution is the $\delta E_{loss}$.

\textcolor{blue}{  TO DO HERE: make sure we have the geometry right, cause otherwise this correction is meaningless.}

\begin{comment}
dE/dxi                  => ?dE/dxi MC Reco - Data comparison
dxi                        => ?dxi      MC Reco - Data comparison
?TOT, ?i<j                  => Efficiency correction
\end{comment}
